---
title: "Coupling Coordination Degree Model and Metacoupling Analysis"
author: "Wenbo Lyu"
date: |
  | Last update: 2026-05-11
  | Last run: `r Sys.Date()`
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{ccd}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  message = FALSE,
  comment = "##",
  fig.path = "man/figures/ccd/"
)
```

# Introduction

The **Coupling Coordination Degree (CCD) model** is widely used to quantify the degree of coupling and coordinated development among multiple subsystems. Originating from physics, it has been extensively applied in regional and human–environment systems.

## Coupling Degree

Given *n* normalized subsystem indicators $U_i$, the standard coupling degree $C$ is defined as:

$$
C = \left[ \frac{\prod_{i=1}^{n} U_i}{\left( \frac{1}{n} \sum_{i=1}^{n} U_i \right)^n} \right]^{\frac{1}{n}}
$$

Although widely used, this formulation may suffer from **scale sensitivity and over-amplification effects** due to the power structure. To address these issues, several formulations have been proposed by modifying the functional form of the coupling degree.

## Modified Coupling Degree

### Modification by $\text{wang et al}^{[1]}$.

**First**, Wang et al. introduce a formulation that incorporates pairwise differences among subsystems while normalizing their relative magnitudes:

$$
C = \sqrt{\left[1-\frac{\sum\limits_{i>j,j=1}^{n-1} \sqrt{\left(U_i-U_j\right)^2}}{\sum_{m=1}^{n-1}m}\right] \times \left(\prod_{i=1}^n \frac{U_i}{\text{max} U_i}\right)^{\frac{1}{n-1}}}
$$

### Modification by $\text{fan et al}^{[2]}$.

**Alternatively**, Fan et al. propose a simplified structure derived from variance-like dispersion, which directly captures the imbalance among subsystem indicators:

$$
C = 1-2\sqrt{\frac{n\sum_{i=1}^n U_i^2 - \left(\sum_{i=1}^n U_i\right)^2}{n^2}}
$$

## Comprehensive Development Index

The overall development level is defined as:

$$
T = \sum_{i=1}^{n} \alpha_i U_i
$$

where $\alpha_i$ are weights with $\sum \alpha_i = 1$.

## Coordination Degree

The coordination degree $D$ integrates interaction $C$ and development $T$:

$$
D = \sqrt{C \times T}
$$

where  
- $C$ measures coupling degree  
- $T$ measures development level  
- $D$ reflects coordinated development  

## Metacoupling Perspective

The CCD framework can be extended under the $\text{metacoupling framework}^{[3,4]}$, distinguishing:

- **Intracoupling**  
- **Pericoupling**  
- **Telecoupling**  

This enables cross-scale analysis of coupling.

# Example Cases

## Install necessary packages and load data

```{r install_pkgs, eval = FALSE, echo = TRUE}
install.packages(c("sdsfun", "coupling", "tidyr", "dplyr", "ggplot2"), dep = TRUE)
```

The `gzma` dataset represents the *Data of Social Space Quality in Guangzhou Metropolitan Areas of China (2010)*. It contains multiple indicators describing urban social space conditions. In particular, four key variables correspond to subsystem scores, including population stability (`PS_Score`), educational level (`EL_Score`), occupational hierarchy (`OH_Score`), and income level (`IL_Score `).

Load the `gzma` dataset from the `sdsfun` package:

```{r load_data}
gzma = sf::read_sf(system.file('extdata/gzma.gpkg',package = 'sdsfun'))
gzma
```

Normalize the `*_Score` columns:

```{r normalize_score}
dt = apply(sf::st_drop_geometry(gzma), 2,
           \(.x) (.x - min(.x)) / (max(.x) - min(.x)))
head(dt)
```

## Analysis of coupling coordination degree

```{r ccd_standard}
ccd_standard = coupling::ccd(dt)
head(ccd_standard)
```

```{r ccd_wang}
ccd_wang = coupling::ccd(dt, method = "wang")
head(ccd_wang)
```

```{r ccd_fan}
ccd_fan = coupling::ccd(dt, method = "fan")
head(ccd_fan)
```

```{r fig_ccd,fig.width=4.5,fig.height=6.5,fig.dpi=300,fig.cap=knitr::asis_output("**Figure 1**. Spatial distribution of CCD components across three estimation methods. Panels display component C and component D derived from the standard, Wang, and Fan methods, respectively.")}
ccd_df = do.call(cbind, list(ccd_standard, ccd_wang, ccd_fan))
names(ccd_df) = paste0(rep(c("standard", "wang", "fan"), each = 2),
                       "_", rep(c("C", "D"), times = 3))
fig1 = ccd_df |> 
  sf::st_set_geometry(sf::st_geometry(gzma)) |> 
  tidyr::pivot_longer(-geometry, names_to = "var", values_to = "val") |> 
  dplyr::mutate(var = factor(var, levels = names(ccd_df))) |> 
  ggplot2::ggplot() +
  ggplot2::geom_sf(ggplot2::aes(fill = val), color = "grey40", lwd = 0.15) +
  ggplot2::scale_fill_gradientn(
    name = "degree",
    colors = c("#ffffcc", "#d9f0a3", "#addd8e",
               "#78c679", "#31a354", "#006837")
  ) +
  ggplot2::facet_wrap(~var, ncol = 2) +
  ggplot2::theme_bw(base_family = "serif") +
  ggplot2::theme(
    panel.grid = ggplot2::element_blank(),
    axis.text = ggplot2::element_blank(),
    axis.ticks = ggplot2::element_blank(),
    strip.text = ggplot2::element_text(face = "bold", size = 15),
    legend.title = ggplot2::element_text(size = 16.5),
    legend.text = ggplot2::element_text(size = 15)
  )
fig1
```

## References

[1] Wang, S., Kong, W., Ren, L. and ZHI, D., 2021. Research on misuses and modification of coupling coordination degree model in China. Journal of Natural Resources, 36, 793-810. https://doi.org/10.31497/zrzyxb.20210319

[2] Fan, D., Ke, H. and Cao, R., 2024. Modification and improvement of coupling coordination degree model. Stat. Decis, 40, 41-46. https://doi.org/10.13546/j.cnki.tjyjc.2024.22.007

[3] Tang, P., Huang, J., Zhou, H., Fang, C., Zhan, Y., Huang, W., 2021. Local and telecoupling coordination degree model of urbanization and the eco-environment based on RS and GIS: A case study in the Wuhan urban agglomeration. Sustainable Cities and Society 75, 103405. https://doi.org/10.1016/j.scs.2021.103405

[4] Li, Y., Jia, N., Zheng, L., Yin, C., Chen, K., Sun, N., Jiang, A., Wang, M., Chen, R., Zhou, Z., 2026. A meta-coupling analysis between three-dimensional urbanization and ecosystem services in China’s urban agglomerations. Communications Earth & Environment 7. https://doi.org/10.1038/s43247-025-03047-w
